full title

### 2020-11-21 paper/pldi21/javascript.tex
Fixed minor typo

We define the sealed symbolic states by not only extending the concrete values
$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult for static analysis to know whether strong udpates are possible or not.
To check the possibility of strong updates during sealed symbolic execution,
we augment its states with the abstract counters $\abscountset$.

>>>>

We define the sealed symbolic states by not only extending the concrete values
$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult for static analysis to know whether strong updates are possible or not.
To check the possibility of strong updates during sealed symbolic execution,
we augment its states with the abstract counters $\abscountset$.
